Estimation of Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra with the Hydrogen Epoch of Reionization Array

### 2015-12-09 ForegroundSimulations/notes.tex
Add three figures and notes.tex, notes.pdf to repo
From 1ff4129 (master):
=====================

(*) Add three figures and notes.tex, notes.pdf to git repo. These
figures go into the notes and are meant to illustrate initial findings
from simulations of delay spectra of foregrounds and EoR signal. It is
meant to be used for stimulating discussions on how much we understand
our signal and foregrounds.

>>>>

Figure~\ref{fig:simulated-visibilities} shows the simulated visibilities from foregrounds, the redshifted H~{\sc i} fluctuations, and residual foregrounds visibilities after deconvolution along the delay axis. The black curves indicate visibilities obtained with an achromatic antenna power pattern (does not change with frequency over the entire bandwidth) while the gray curves are the corresponding visibilities for a chromatic beam. The solid lines in black and gray denote foreground visibilities. The dashed curves in the same colors denote visibilities from simulated redshifted H~{\sc i} fluctuations, and the dotted-dashed lines denote the residual visibilities obtained after deconvolution of the foreground delay spectra. The orange curve denotes a wideband Blackman-Harris window applied to the foreground visibilities to produce delay spectra which were subsequently deconvolved to obtain the residual visibilities. The red, blue and green curves denote the narrowband Blackman-Harris window weights centered on 150, 160 and 170~MHz each of effective bandwidth $\simeq 10$~MHz that will be applied to the simulated EoR H~{\sc i} signal and the foregrounds (both simulated and residual visibilities).

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{simulated_FG_EoR_visibilities.eps}
\caption{Simulated EoR H~{\sc i} and foreground visibilities over 100~MHz bandwidth for a 14.6~m baseline of HERA. \label{fig:simulated-visibilities}}
\end{figure}

Figure~\ref{fig:wideband-delay_spectrum} shows the delay spectra of simulated foreground visibilities (in orange) obtained with chromatic (dashed) and achromatic (solid) beams both weighted with the wideband Blackman-Harris window functions in the spectrum, the corresponding CLEAN components in gray and the residuals in black. The depth of deconvolution is set by the limit at which the rms of the residuals inside the horizon limits becomes equal to that on the outside. It is observed that the visibilities simulated with chromatic power pattern (dashed orange) are significantly broadened in delay spectra due to the additional chromaticity. The delay deconvolution is restricted to the {\it foreground wedge} with three additional delay bins on either side of the wedge. Due to this restriction, the residuals inside the horizon delay limits are lower than those outside. Since the simulated visibilities obtained using the achromatic power pattern are predominantly contained well within the horizon delay limits, the delay-domain deconvolution of these delay spectra is much more effective at lowering the residuals (by $\sim 2$ orders of magnitude) than in the case of visibilities obtained with a chromatic power pattern. These delay spectrum residuals correspond to the visibility residuals plotted in Figure~\ref{fig:simulated-visibilities}.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{wideband_simulated_FG_delay_spectrum.eps}
\caption{. \label{fig:wideband-delay_spectrum}}
\end{figure}

Figure~\ref{fig:subband-delay_spectrum} shows the delay spectra of the simulated EoR H~{\sc i} fluctuations and the foregrounds. The three panels show the three different center frequencies (150, 160, and 170~MHz) around which the delay spectra were obtained using the narrow band Blackman-Harris window functions shown earlier in Figure~\ref{fig:simulated-visibilities}. Delay spectra obtained using chromatic and achromatic antenna power patterns are shown in black and gray colors respectively. The dashed lines denote delay spectra of foreground residuals obtained after complex delay-domain deconvolution under the concept of foreground removal. The dotted lines denote the foreground delay spectra obtained under the concept of foreground avoidance where foregrounds were not removed but simply down-weighted by the narrowband Blackman-Harris window unctions.

\begin{figure}[htb]
\centering
\includegraphics[width=\linewidth]{subband_simulated_EoR_FG_delay_spectrum.eps}
\caption{. \label{fig:subband-delay_spectrum}}
\end{figure}

It is noticed from Figure~\ref{fig:simulated-visibilities} that the foregrounds are about 5 orders of magnitude brighter than the EoR H~{\sc i} fluctuations in the visibilities. From Figure~\ref{fig:subband-delay_spectrum} it is seen that the foreground visibilities under foreground avoidance and their residuals under foreground removal are still brighter than the EoR signal. The delay spectra of foreground residuals however are much closer in magnitude to the EoR signal (to a factor $\lesssim 10$) at $|\tau| \gtrsim 200$~ns.
